---
output: html_notebook
---

#### Creating Descriptive Statistics - Demo
<br>

1. How many cars of each type of transmission? <br>
2. What does fuel economy look like? <br>
3. How are cylinders and fuel economy related? <br>

```{r}
cars <- read.csv("Cars.csv")
head(cars)
```
<br>
**1. How many cars of each type of transmission?**

```{r}
# Create a frequency table
table(cars$Transmission)
```

<br>
**2. What does fuel economy look like? Miles per galon** <br>

```{r}
# Get the minimum value
min(cars$Fuel.Economy)
```

```{r}
# Get the maximum value
max(cars$Fuel.Economy)
```

```{r}
# Get the average value
mean(cars$Fuel.Economy)
```

```{r}
# Get the median value
median(cars$Fuel.Economy)
```

```{r}
# Get the quartiles
quantile(cars$Fuel.Economy)
```

```{r}
# Get the standard deviation
sd(cars$Fuel.Economy)
```

```{r}
# Get the total value
sum(cars$Fuel.Economy)
```
<br>

**3. How are cylinders and fuel economy related?** <br>

```{r}
# Get the correlation coefficient
cor(
    x = cars$Cylinders,
    y = cars$Fuel.Economy)
```

```{r}
# Summarize an entire table
summary(cars)
```

As we can see, the correlation coefficient for these 2 variables is -0. 85, which is a relatively strong inverse correlation. In the event you'd like to summarize an entire table of values, we can use the summarize function and pass in a data frame as an argument. When we summarize a table, it provides us with a summary of each variable, based on the type of variable in each column. 

