---
output: html_notebook
---

### Creating Statistical Models - Demo

1. How are petal lenght and petal width related? <br>
2. Can we predict new petal width values? <br>

```{r}
# Load the data
data(iris) #iris is a sample dataset
head(iris)
```

```{r}
# Create a scatterplot
plot(
    x = iris$Petal.Length, 
    y = iris$Petal.Width,
    main = "Iris Petal Length vs. Width",
    xlab = "Petal Length (cm)",
    ylab = "Petal Width (cm)")
```
We want to draw a line of best fit through the center of this set of points. 

<br>
```{r}
# Create a linear regression model
model <- lm(
    formula = Petal.Width ~ Petal.Length,
    data = iris)
summary(model)
```
**lm()** createa a new Lineal regression model
<br>

```{r}
# Draw a regression line on plot
plot(
    x = iris$Petal.Length, 
    y = iris$Petal.Width,
    main = "Iris Petal Length vs. Width",
    xlab = "Petal Length (cm)",
    ylab = "Petal Width (cm)")
lines(
    x = iris$Petal.Length,
    y = model$fitted, 
    col = "red",
    lwd = 3)
```

```{r}
# Get correlation coefficient
cor(
    x = iris$Petal.Length,
    y = iris$Petal.Width)
```
The correlation coefficient is 0. 96. This means that there's a relatively high correlation between Petal Length and Petal Width. This high correlation, combined with the goodness of fit of our linear regression model, tells us that Petal. Length will likely be a good predictor variable for Petal. Width.
<br>

```{r}
# Predict new values from the model
predict(
    object = model, 
    newdata = data.frame(
        Petal.Length = c(2, 5, 7)))
```
For a Petal Length of 2 cm, our linear model predicted a Petal Width of 0. 46 cm. For a Petal Length of 5 cm, it predicted a Petal Width of 1. 71 cm. And for a Petal Length of 7 cm, it predicted a Petal Width of 2. 54 cm.